\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}



% ----- Fonts (XeLaTeX/LuaLaTeX) -----
\setmainfont{Times New Roman}

% ----- Spacing -----
\setstretch{1.05}
\setlength{\parindent}{0pt}

% ----- Headings style -----
\titleformat{\section}{\Large\bfseries}{\thesection}{0.75em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{0.75em}{}
\titlespacing*{\section}{0pt}{10pt}{6pt}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}

% ----- Lists -----
\setlist[itemize]{leftmargin=1.2em, itemsep=3pt, topsep=4pt}
\setlist[enumerate]{leftmargin=1.2em, itemsep=3pt, topsep=4pt}

% ----- Table helpers -----
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

% ----- Small label for "Key Principle" -----
\newcommand{\keylabel}[1]{\textbf{#1}}

% ----- Button style -----
\newcommand{\btn}[1]{%
  \tcbox[
    on line,
    boxsep=2pt,
    left=6pt,right=6pt,top=3pt,bottom=3pt,
    colback=white,
    colframe=black,
    arc=2pt
  ]{\textbf{#1}}%
}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black,
  citecolor=black
}

\begin{document}

\begin{center}
{\LARGE \textbf{AI Matchmaking for Proof of Talk}}\\[4pt]
{\large \textit{Connecting 2,500 Decision-Makers with the Right People}}
\end{center}

\section*{The Problem}

Proof of Talk brings 2,500 leaders (approximately \$18T AUM) into one room, but high-value connections are still missed. Attendees often lack a fast way to identify the \textit{right} counterpart (capital $\leftrightarrow$ deal, bank $\leftrightarrow$ compliant infrastructure, buyer $\leftrightarrow$ seller) before the event begins. The value is not attendance volume but rather it is the quality of meetings.

\section*{The Solution}

Build an AI system that learns who each person is and what they need, then suggests 5--8 high-value matches before they even arrive.

\section*{What Makes a Valuable Match?}

This isn't a directory where you browse similar people. A valuable match creates potential for actual business outcomes: an investment opportunity (LP meets GP, investor meets founder), a partnership fit (bank meets custody provider), a buyer-seller relationship (institution seeking tokenization meets tokenization platform), or a critical dependency (protocol needing compliance infrastructure meets compliance-focused Layer 2). The system identifies connections where one party has what the other needs.

\keylabel{Key Principle:} Match complementary people, not similar people.

\begin{itemize}
  \item Connect investors with founders, not investors with investors
  \item Connect solution providers with people who have that problem
  \item Connect buyers with sellers, not competitors with competitors
\end{itemize}

\section*{How It Works}

\begin{center}
\begin{tabularx}{\textwidth}{|Y|Y|Y|Y|}
\hline
\textbf{1. COLLECT} & \textbf{2. ANALYZE} & \textbf{3. MATCH} & \textbf{4. DELIVER} \\
\hline
Registration \quad LinkedIn \quad Company data \quad Social media &
AI reads \& understands \quad Extracts goals \quad Identifies needs &
Scores connections \quad Finds complementary pairs \quad Ranks by value &
Personalized dashboard \quad 5--8 top matches \quad With explanations \\
\hline
\end{tabularx}
\end{center}

\subsection*{Step 1: Collect Rich Data}

We gather information from multiple sources:
\begin{itemize}
  \item Registration form (self-reported role, goals, offers, and focus areas)
  \item Public company webpage snippet via \texttt{company\_url} (opt-in; publicly available text)
  \item \textit{Production upgrade (with consent + API access):} LinkedIn profiles and X/Twitter signals for richer enrichment
\end{itemize}


\subsection*{Cold Start: Making It Work with Minimal Data}

For new attendees or those with limited public data, we ask 3 simple questions during registration:
\begin{enumerate}
  \item ``What are you looking for at this event?'' (e.g., institutional LPs, compliant custody solutions, tokenization partners)
  \item ``What can you offer to others?'' (e.g., capital allocation, technical infrastructure, regulatory expertise)
  \item ``Pick your top 3 focus areas'' from a curated list (RWA tokenization, DeFi infrastructure, institutional custody, regulatory frameworks, ZK tech, etc.)
\end{enumerate}

These three questions give the system enough signal to make useful matches even without LinkedIn scraping.

\subsection*{Step 2: Profile Understanding (Prototype NLP)}

The prototype builds a structured profile from the attendee’s text fields (\texttt{focus}, \texttt{looking\_for}, \texttt{offers}, \texttt{tags}) using lightweight NLP (TF-IDF + keyword normalization):
\begin{itemize}
  \item Extract the attendee’s main themes and focus areas (beyond job title)
  \item Represent needs (\texttt{looking\_for}) and offerings (\texttt{offers}) as comparable text signals
  \item Support matching with transparent, interpretable features (similarity + role fit + overlap)
\end{itemize}

\textit{Production upgrade:} embeddings/LLMs can enrich profiles from longer bios and consented external sources.

\subsection*{Step 3: Smart Matching Scoring Algorithm}

\textbf{Final Match Score =}
\begin{itemize}
  \item 40\% \textbf{Complementarity (two-way):} 
  $0.5\cdot \mathrm{sim}(A_{\text{wants}}, B_{\text{offers}}) + 0.5\cdot \mathrm{sim}(B_{\text{wants}}, A_{\text{offers}})$
  \item + 30\% \textbf{Role Compatibility:} natural counterparty pairs (Investor$\leftrightarrow$Founder, Operator$\leftrightarrow$Founder, Investor$\leftrightarrow$Operator)
  \item + 20\% \textbf{Topic Overlap:} shared focus areas (e.g., RWA, custody, DeFi, ZK, identity, compliance)
  \item + 10\% \textbf{Diversity Boost:} small novelty factor to surface non-obvious but high-value connections
\end{itemize}

\subsection*{Real Example}

\begin{longtable}{L{2.6cm}L{3.0cm}L{3.2cm}L{3.2cm}L{3.3cm}}
\toprule
\textbf{Name} & \textbf{Role} & \textbf{Company Type} & \textbf{What They Have} & \textbf{What They Need} \\
\midrule
Sarah & Managing Director & Sovereign Wealth Fund & Capital to invest & Regulated tokenization platforms \\
Marcus & CEO & Tokenization Startup & Real estate tokenization platform & Institutional investors \\
Elena & Head of Digital Assets & European Bank & Bank infrastructure \& clients & Custody tech, compliance solutions \\
Kenji & CTO & Layer 2 Protocol & Compliant blockchain infrastructure & Enterprise customers \\
Aisha & GP & Crypto VC Fund & Investment capital & Deal flow, co-investors, LPs \\
\bottomrule
\end{longtable}

Basic system: Matches Sarah with Marcus (obvious connection)

Smart system: Also connects Kenji (compliance tech) with Elena (bank needing compliance), and suggests Aisha could fund Marcus while Sarah becomes Aisha's LP. Three deals from five people.

\section*{What Attendees See}

Each person gets a personalized web dashboard 3 days before the event with 5--8 carefully selected matches.

\begin{tcolorbox}[
  colback=white,
  colframe=black,
  boxrule=0.6pt,
  arc=2pt,
  left=10pt,right=10pt,top=10pt,bottom=10pt
]
\textbf{Marcus Weber}\\
CEO, TokenizeNow \quad \textbullet \quad Tokenization Platform\\[8pt]

\textbf{Why this match?}\\
You're exploring institutional allocation to tokenized real-world assets. Marcus's platform tokenizes real estate and private credit on-chain, and he's actively seeking institutional investors. Direct product-to-capital fit.\\[8pt]

\textbf{Conversation starters:}
\begin{itemize}
  \item What regulatory frameworks have you navigated?
  \item Which asset classes see the most traction?
\end{itemize}

\btn{Request Introduction}\hspace{10pt}\btn{Save for Later}
\end{tcolorbox}

\section*{Privacy \& Consent}

We take data privacy seriously with a tiered consent model:
\begin{itemize}
  \item \textbf{Default (works for everyone):} Matching uses only registration form data --- the three questions you answer plus basic info like company and role
  \item \textbf{Opt-in enrichment:} Check a box to allow the system to enrich your profile using public LinkedIn, company website, and social media. Better matches, but you control it.
  \item \textbf{Stealth mode:} For high-profile attendees (regulators, sovereign fund managers, public figures). Your profile is visible only at a high level (``Managing Director, Sovereign Wealth Fund'') and introductions require your manual approval. You still get matches, but you're not searchable.
\end{itemize}

\section*{Technology Stack}

We're keeping the tech stack simple and realistic for a prototype:

\begin{tabular}{L{4.0cm}L{11.0cm}}
\toprule
\textbf{Component} & \textbf{Technology} \\
\midrule
AI Matching & TF-IDF + weighted scoring (two-way complementarity) \\
Data Processing & Python (pandas, scikit-learn) \\
External Retrieval & requests + BeautifulSoup (public web snippet via \texttt{company\_url}) \\
Data Store & CSV file (\texttt{attendees.csv}) with fictional profiles \\
Web App & Streamlit (Python) \\
Hosting & Streamlit Community Cloud + GitHub \\
\bottomrule
\end{tabular}


\subsection*{Why these choices?}

\begin{itemize}
  \item \textbf{TF-IDF + weighted scoring:} Fast, interpretable baseline for matching needs/offers/tags; easy to debug and explain.
  \item \textbf{Python:} Strong ecosystem for data handling and ML prototyping (pandas, scikit-learn).
  \item \textbf{Streamlit:} Quick way to ship a usable web prototype with minimal UI overhead.
  \item \textbf{Public web retrieval (requests + BeautifulSoup):} Demonstrates external enrichment using opt-in, publicly available page text.
  \item \textbf{CSV data store:} Simple and sufficient for a small fictional dataset in a case-study prototype.
\end{itemize}

\textbf{Future enhancement:} Upgrade to embeddings (e.g., pgvector) and add an organizer dashboard for importing attendees and managing introductions. Not needed for the MVP.


\section*{Why This System is Different}

\begin{tabular}{L{4.0cm}L{5.5cm}L{5.5cm}}
\toprule
\textbf{Feature} & \textbf{Standard Platforms} & \textbf{Our System (Prototype)} \\
\midrule
Data Sources & Registration only & Registration-style fields + opt-in public web snippet \\
Matching Logic & Keyword overlap / similar profiles & Complementary matching (want$\leftrightarrow$offer) + role fit \\
Match Quality & 20--50 broad matches & 5--8 curated, high-intent matches \\
Scoring Model & None or simple tags & Transparent 4-factor weighted scoring (with breakdown) \\
Explanations & Often limited or none & Clear reasons per match + conversation starters \\
\bottomrule
\end{tabular}

\section*{Project Links}

\begin{itemize}
   \item \textbf{Figma Wireframe:} \href{https://www.figma.com/make/LiC9Hy2rV2pn94FGHeMVFU/Sibonile-Prototype-Figma?p=f&t=wwSHxT0YL52CV0A8-0&fullscreen=1}{Figma Prototype}  \item \textbf{Streamlit Prototype:} \href{https://potaimatchmaking-cjhux4hc8yh4pweadh4yrk.streamlit.app/}{potaimatchmaking.streamlit.app}
  \item \textbf{GitHub Repository:} \href{https://github.com/Sibonile7/pot_ai_matchmaking}{github.com/Sibonile7/pot\_ai\_matchmaking}
\end{itemize}

\end{document}
